Concurrent Programming with Harmony

### 2020-07-28 book/paper.tex
Fixed invariant checking

We can do this by adding another process that, in a loop,
checks the invariant.  \autoref{fig:tasinv} shows the code.
Method \texttt{checkInvariant()} checks to see if the invariant holds
in a state.  It introduces a new feature of Harmony: the ability to have
variables local to a method.  In this case, the process variable \textit{sum}
is used to compute the number of shared variables that have value
\texttt{False}.
The function is invoked by in a loop by a process that runs alongside
the other processes.
In Harmony, \textbf{assert} statements are executed atomically, so the
evaluation of the assertion is not interleaved with the execution
of other processes.
Because Harmony tries every possible execution, the process is guaranteed
to find violations of the invariant if it does not hold.

>>>>

We can do this by adding another process that
checks the invariant.  \autoref{fig:tasinv} shows the code.
Method \texttt{checkInvariant()} checks to see if the invariant holds
in a state.  It introduces a new feature of Harmony: the ability to have
variables local to a method.  In this case, the process variable \textit{sum}
is used to compute the number of shared variables that have value
\texttt{False}.
The method is invoked by a process that runs alongside
the other processes.
In Harmony, \textbf{assert} statements are executed atomically, so the
evaluation of the assertion is not interleaved with the execution
of other processes.
Because Harmony tries every possible execution, the process is guaranteed
to find violations of the invariant if it does not hold.
